\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}
% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}


\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\residue}{\mathbb{Z}/n\mathbb{Z}}
\newcommand{\prob}[1]{\section*{#1}}


\begin{document}

\prob 1 

Prove that \( |GL_2(\mathbb{F}) |= 6 \)


\prob 2

Write out all the elements of \(GL_2 (F_2) \) and compute the order of each element.

\prob 3 Show that \( GL_2 ( \F  ) \) is non-abelian.

\prob 4

Show that if n is not prime then \(\residue\) is not a field. 

\prob 5 

Show that \(GL_n(F)\) is a finite group if and only if F has a finite number of elements


\prob 6

If \(|F| = q\) is finite prove that \(GL_n(F) < q^{n^2}\).

\prob 7 

Let p be a prime.
Prove that the order of \(GL_2 (\F_p) \) is \(p^4 -p^3 -p^2 + p\). 
(do not just quote the order formula in this section). 
[Subtract the number of 2 x 2 matrices over \(\F_p\). 
You may use tha fact that a 2 x 2 matricx is not invertible if and only if one row is a muliple of the other. ]

\prob 8

Show that \(GL_n(F)\) is non-abelian for any \(n \ge 2\) and any F. 


\prob 9 

Prove that the binary operation of matrix muliplication of 2 x 2 matricies iwth real entities is associative


\prob {10}
Let \(H(F) = \{\begin{bmatrix}
1 & a & b \\
0 & 1 & c \\
0 & 0 & 1
\end{bmatrix} | a, b, c, d \in F\}\) -- called the Heisenberg group over F. Let 
\(X = \begin{bmatrix}
    1 & a & b\\
    0 & 1 & c\\
    0 & 0 & 1
\end{bmatrix}\) and \(Y = \begin{bmatrix}
    1 & d & e\\
    0 & 1 & f \\
    0 & 0 & 1
\end{bmatrix}\) be elements of \(H(F)\).

\begin{enumerate}
    \item Compute the matrix product \(XY\) and deduce that \(H(F)\) is closed under matrix multiplication. 
    Exhibit explicit maricies such that \(XY  \not = Y X\) (so that \(H(F)\) is always non-abelian).
    \item Find and explicit formula for the matrix inverse \(X^{-1}\) and deduce that \(H(F)\) is closed under inverse.
    \item Prove the associative law for \(H(F)\) and deduce that \(H(F)\) is a group of order \(|F|^3\). 
    \item Find the order of each element of the finite group \(H(\Z / 2 \Z)\).
    \item Prove that every nonidentity elements of the group \(H (\R )\) has infinite order.
\end{enumerate}


\end{document}